Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
Strip out more references to software availability

Each article was rated on a 0 -- 3 scale for its software, data and code availability.
'Software availability' rated how freely and openly available the software used was.
It was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
'Code availability' rated how easily and openly available the computational methods used in the article were.
Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
readODS::read_ods(
    system.file(
      "extdata",
      "Reproducibility_in_plant_pathology_notes.ods",
      package = "Reproducibility.in.Plant.Pathology"
    ),
    na = "NA",
    sheet = "scoring_criteria_paper"
  ) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Articles were three in three areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
```

>>>>

Each article was rated on a 0 -- 3 scale for its data and code availability.
'Code availability' rated how easily and openly available the computational methods used in the article were.
Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
readODS::read_ods(
    system.file(
      "extdata",
      "Reproducibility_in_plant_pathology_notes.ods",
      package = "Reproducibility.in.Plant.Pathology"
    ),
    na = "NA",
    sheet = "scoring_criteria_paper"
  ) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Articles were three in two areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of two areas, 'Computational Methods Availability' and 'Data Availability'.")
```
